Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-03-04 paper.tex
Add acknowledgement of DiRAC

>>>>

This work used the DiRAC Extreme Scaling service at the University of Edinburgh, operated by the Edinburgh Parallel Computing Centre on behalf of the STFC DiRAC HPC Facility (www.dirac.ac.uk), specifically Thematic Project allocation ACTP245. This equipment was funded by BEIS capital funding via STFC capital grant ST/R00238X/1 and STFC DiRAC Operations grant ST/R001006/1. DiRAC is part of the National e-Infrastructure.
